Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-16 VMCAI-revised-version/final.tex
up

Since {\sc $t$-liveness} is undecidable, from Proposition~\ref{reductions},  we deduce that {\sc State-resilience} is undecidable  for reset-VASS, which are WSTS with strong upward-compatibility. Hence {\sc State-resilience} is undecidable  for WSTS with strong upward-compatibility.

@@

\begin{proof}
We consider in VASS the case of when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).\]
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable. 
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^{2d}$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \qed
\end{proof}

>>>>

Since {\sc $t$-liveness} is undecidable, from Proposition~\ref{reductions},  we deduce that {\sc State-resilience} is undecidable  for reset-VASS, which are WSTS with strong upward-compatibility.

@@

\begin{proof}
We consider in VASS the case of when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
We want to use the fact that
it is decidable whether $\post^*(X) \subseteq \pred^*(Y)$ when 
$X$ and $Y$ are both semilinear sets~\cite{DBLP:journals/corr/abs-2207-02697}.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad \text{iff} \quad \Bad \subseteq \pred^*(\Safe).\]
and hence, {\sc Resilience} is decidable. 
The reachability relation of integer $d$-VASS is definable by a well-formed formula with no free variables in the first-order theory of the integers with addition and orders (Presburger arithmetic) in $\mathbb{Z}^{2d}$, hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \qed
\end{proof}
